Higher-Order unification for free!

### 2024-04-18 paper/main.tex
remove todo
correct a cref

\noindent
\todo{remove pruning optimization from code above}

@@

First and foremost, problematic terms stored in
\linkStore have to be moved back into the game:
a suspended link must be turned into a valid assignment.
This operation is possible thanks to \fullref{inv:linklhs},
which ensures that no link causes an occur-check~(\ref{sec:oc})
and the fact that \linkStore is duplicate-free (\cref{TODO}).

>>>>

% \noindent
% \todo{remove pruning optimization from code above}

@@

First and foremost, problematic terms stored in
\linkStore have to be moved back into the game:
a suspended link must be turned into a valid assignment.
This operation is possible thanks to \fullref{inv:linklhs},
which ensures that no link causes an occur-check~(\ref{sec:oc})
and the fact that \linkStore is duplicate-free (see \cref{sec:invariant1}).
